\documentclass[11pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8x]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{layout}
\usepackage{txfonts}
\usepackage{geometry}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}
\geometry{a4paper,left=15mm,right=10mm, top=1cm, bottom=1.4cm}
\usepackage{float}
\usepackage{listings}
\usepackage[colorlinks=true, allcolors=Blue]{hyperref}
\usepackage{caption}
\usepackage{booktabs} %allows for short midlines
%\usepackage{subcaption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Application letter}
\author{Tijl Jappens}

\begin{document}
\maketitle
Dear Hiring Manager,\\\\
I am writing to express my interest in the position of Postdoctoral Researcher in Theory of Quantum Systems and Quantum Computers at Imec. I am a highly motivated researcher finishing my PhD degree at the institute for theoretical physics at KU Leuven. My research focuses on topological phases of quantum matter, and I have authored two manuscripts currently under review in Communications in Mathematical Physics (see attached CV), with a third manuscript in progress.\\\\
In addition to my research experience, I have some mentoring experience. I have some experience guiding bachelor students with their thesis and have frequently been a teaching assistant. I have also worked collaboratively in multicultural teams at KU Leuven, which has honed my communication and team player skills.\\\\
My research has made me proficient in many mathematical tools used in the analyses of quantum many body physics. I am also fluent in English, which is essential for working at an international organization like Imec.\\\\
The large amount of seminars (including some from imec researchers) and lectures during the period of my PhD made me passionate about many of the aspects of quantum mechanics, including quantum computing. I believe that my skills and experience make me a strong candidate for this position. I am excited about the opportunity to contribute to Imec's cutting-edge research in this field.\\\\
Thank you for considering my application. I look forward to hearing from you.\\\\
Sincerely,\\
Tijl Jappens
\end{document}
