\documentclass[11pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8x]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{layout}
\usepackage{txfonts}
\usepackage{geometry}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}
\geometry{a4paper,left=15mm,right=10mm, top=1cm, bottom=1.4cm}
\usepackage{float}
\usepackage{listings}
\usepackage[colorlinks=true, allcolors=Blue]{hyperref}
\usepackage{caption}
\usepackage{booktabs} %allows for short midlines
%\usepackage{subcaption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Application letter}
\author{Tijl Jappens}

\begin{document}
\maketitle
Dear Hiring Manager,\\\\
Let me introduce myself. I am Tijl, I finished my PhD in mathematical physics at the KU Leuven. My research focused on topological phases of quantum matter, and I have authored two manuscripts, one accepted and one currently under review in Communications in Mathematical Physics (see attached CV), with a third manuscript in progress.\\\\
I am now however looking for a new challenge outside of academia. I am looking for a job near to Leuven (I noticed .ocean doesn't have open vacancies there, that is why I am applying with a spontaneous application). My research has made me proficient in many mathematical tools used in simulating and analysing physical systems (both numerically and analytically). If you have any vacancies going in this direction, please let me know. I would also be very interested in a position that requires me to learn various computer science/engineering concepts on the go, I am a quick learner and am very motivated to learn more about them.\\\\
In addition to my research experience, I have some mentoring experience. I have some experience guiding bachelor students with their thesis and have frequently been a teaching assistant. I have also worked collaboratively in multicultural teams at KU Leuven, which has honed my communication and team player skills.
\\\\
Thank you for considering my application. I look forward to hearing from you.\\\\
Sincerely,\\
Tijl Jappens
\end{document}
