\documentclass[11pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8x]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{layout}
\usepackage{txfonts}
\usepackage{geometry}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}
\geometry{a4paper,left=15mm,right=10mm, top=1cm, bottom=1.4cm}
\usepackage{float}
\usepackage{listings}
\usepackage[colorlinks=true, allcolors=Blue]{hyperref}
\usepackage{caption}
\usepackage{booktabs} %allows for short midlines
%\usepackage{subcaption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Application letter}
\author{Tijl Jappens}

\begin{document}
\maketitle
Dear Hiring Manager,\\\\
I am writing to express my interest in the position of Quantitative Energy Market Analyst at Engie. I am a researcher finishing my PhD degree at the institute for theoretical physics at KU Leuven. My research focuses on topological phases of quantum matter, and I have authored two manuscripts, one accepted and one currently under review in Communications in Mathematical Physics (see attached CV), with a third manuscript in progress.\\\\
In addition to my research experience, I have some mentoring experience. I have some experience guiding bachelor students with their thesis and have frequently been a teaching assistant. I have also worked collaboratively in multicultural teams at KU Leuven, which has honed my communication and team player skills.\\\\
My research has made me proficient in many mathematical tools used in simulating and analyzing physical systems (both numerically and analytically). I have however no experience with economical simulations. I am however very motivated to learn about these and other concepts and would cherish the opportunity to learn and apply new techniques.
\\\\
Thank you for considering my application. I look forward to hearing from you.\\\\
Sincerely,\\
Tijl Jappens
\end{document}
