\documentclass[12pt,a4paper,twoside]{article}

\usepackage[margin=0.7in]{geometry}
\title{Job interview vragen}
\author{Tijl Jappens\footnote{Institute for Theoretical Physics, Katholieke Universiteit Leuven.}}
\date{\today}

\begin{document}
	\maketitle 
	\begin{enumerate}
		\item What makes you unique?\\\\
		I found that during my PhD (and somewhat beyond), I have always been good at finding creative solutions. Once I was done with the beginning phase of learning to read papers and getting a grasp on the basics of mathematical physics, I really found ways to invent new paths to explore and found some creative proofs to certain problems. My promotor has always praised me for being good at this.
		\item Tell me about yourself and your qualifications.\\\\
		I can understand you would think hiring me is a risk. I don't have any practical experience in the kind of computer science you do. In my professional life, I have only used programming to create simulations. Outside of my professional life, the most involved project I ever did was making pong on my android phone (from which I unfortionatly lost the source code, I only have the apk file). I can however promise you, I can learn these things and usually, after I am proficient enough with something, I can be creative and figure out new solutions.
		\item Why do you want to work at this company?\\\\
		You still do some form of research, only a very different type of research then the fundamental research I did before. You research how one can apply certain technologies to some very practical applications. This really fascinates me. In fact, when I started studying, I was doubting between doing engineering and doing physics and it was a very hard choice. In short, I think your company has the kind of professional challenge I am looking for. That is to find a type of research that has an immediate influence on peoples lives and still allows me to apply some form of creative thinking.
		\item What interests you about this role?\\\\
		I think the Internet of Things research nicely captures the above kind of research. It is not the only kind of job I am looking for but it certainly seems to fit.
		\item What motivates you?\\\\
		Being able to do something that doesn't just allow me to follow some kind of standard pattern or procedure but encourages me to be creative and allows me to implement my own ideas.
		\item What are your greatest strengths?\\\\
		I can be very creative with my solutions and am a good analytical thinker.
		\item What are your greatest weaknesses?\\\\
		I am not very good at organising myself in the long term so I guess making a long-term planning is something I am not good at.
		\item What are your goals for the future?\\\\
		I don't have any ambitions like being promoted to management (I don't think I would be good at it). The main goal for me is that I will keep doing projects I like and I find interesting.
		\item Where do you think you'll be in five years?\\\\
		I have no idea. I hope working with you.
		\item What did you like most about your last position?\\\\
		I liked working in theoretical physics. There was an enormous amount of freedom and I was constantly able to challenge my self in learning and applying some very interesting concepts.
		\item What did you like least about your last position?\\\\
		It was a very uncertain job path. The only long term solution is to get a professor position but to obtain it you need to do multiple post docs of only two years and you need to keep moving around the world to get them. I did not want this life. Also, the amount of people that read your work is very limited. Although I submitted my work in some pretty prestigious journals, it still felt like what I did didn't make that much of an impact.
		\item Can you tell me about a difficult work situation and how you overcame it?
		\item How do you respond to stress or change?\\\\
		Well, ask me in a few months as I am completely changing my field of study. No, I think I can handle stress reasonably well. I don't really have problems controlling myself when I speak to large audiences for instance and I can work very effectively right before an important deadline.
		\item How do you handle conflict at work?\\\\
		I never had much conflict at work. The only person I really relied on was my promotor but I always got along with him very well. For the rest, I have had a more senior role for another PhD researcher for my promotor and I have been ok at adapting to this role.
		\item What is your greatest accomplishment?\\\\
		I think my papers.
		\item How do you define success?\\\\
		Doing something that either improves humanity's understanding of something or improves the lives of a particular group of people.
		\item How do your skills align with this role?\\\\
		If you can look besides my obvious lacking of concrete experience, I think you will find I am a good analytical thinker and can be rather versatile.
		\item Why should we hire you?
		\item Why are you leaving your current job?\\\\
		I liked working in theoretical physics. There was an enormous amount of freedom and I was constantly able to challenge my self in learning and applying some very interesting concepts. However, it was a very uncertain job path. The only long term solution is to get a professor position but to obtain it you need to do multiple post docs of only two years and you need to keep moving around the world to get them. I did not want this life. Also, the amount of people that read your work is very limited. Although I submitted my work in some pretty prestigious journals, it still felt like what I did didn't make that much of an impact.
		\item What is your salary range expectation?\\\\
		My current monthly salary is 2650 euro net. I don't expect to earn as much in the coming years. I would fully understand that since I am doing something new, I won't get the same wage as someone that has experience in doing these kind of things.
		\item Do you have any questions?
		\item What are you passionate about?\\\\
		So many things. Technology, mathematics, physics, politics...
		\item What is your teaching philosophy?
		\item What does customer service mean to you?
		\item Tell me about your work experience?
		\item How do you work under pressure?
		\item What is your dream job?
		\item What can you bring to the company?
	\end{enumerate}
\end{document}